% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it M. Carneiro}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.3in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{MAURICIO CARNEIRO}% the \\[12pt] adds a blank line after name


\begin{resume}
(781) 333-8323 \hspace{23 mm} {\small 301 Binney st  \#5040, Cambridge, MA 02142} \hfill carneiro@gmail.com

 
\section{\centerline{EDUCATION}} 
\vspace{8pt} 

{\bf Harvard University} \hfill Cambridge, MA\\
{\sl Ph.D. Computational Biology} \hfill 2010\\

\vspace{-18pt} 
{\bf Oswaldo Cruz Research Institute} \hfill Rio de Janeiro, Brazil\\
{\sl M. Sc. in Molecular Biology} \hfill 2005\\

\vspace{-18pt} 
{\bf Pontifical Catholic University} \hfill Rio de Janeiro, Brazil\\
{\sl B.Sc. in Computer Engineering} \hfill 2003



\section{\centerline{AWARDS}} 
\vspace{8pt} 

{\bf Harvard University} \hfill Cambridge, MA\\
{\sl Distinction in Teaching Award} \hfill 2010\\
{\sl Distinction in Teaching Award} \hfill 2008\\

\vspace{-18pt} 
{\bf ACM International Collegiate Programming Contest} \hfill Beverly Hills, CA\\
{\sl Programming Excellence Award} \hfill  2003\\
{\sl South American Champion} \hfill  2003\\
{\sl 2nd Place of Brazil} \hfill  2002\\

\vspace{-18pt} 
{\bf Pontifical Catholic University} \hfill Rio de Janeiro, Brazil\\
{\sl Best Mathematics Software Award} \hfill 1998


%%\section{\centerline{TECHNICAL SKILLS}} 
%%\vspace{8pt} 

%%{\bf Programming Languages}\\
%%{\sl Proficient: C/C++, LUA, HTML, TeX} \\
%%{\sl Have also used: R, Java, SQL, Assembly, Mathematica, Scheme, PERL, PHP} \\

%%\vspace{-18pt}
%%{\bf Programming Toolkits}\\
%%{\sl worked with: IUP, IUPLUA, BioLUA, BioPERL, SSL, OpenGL, GLUT, GTK, IM} \\

%%\vspace{-18pt}
%%{\bf Languages Spoken}\\
%%{\sl English, Portuguese, Spanish, French} \\

\section{\centerline{PROFESSIONAL EXPERIENCE}} 
\vspace{8pt}

{\bf Broad Institute} \hfill Cambridge, MA \\
{\sl Computational Biologist}  \hfill December 2010 - present  
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Lead the technology development team in the genome sequencing and analysis group
	\item Developed key software tools, using Java and Scala, for medical and population genetics and cancer research.
	\item Worked with the laboratory to develop methods that improve sequencing data statistical analysis 
	\item Defined the data processing pipeline for Pacific Bioscience RS data
\end{itemize}

{\bf M1nd Corporation} \hfill Rio de Janeiro, Brazil \\
{\sl Team Leader}  \hfill November 2004 - May 2006  
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Managed a group of 50 beta testers.
	\item Managed the development of the first location based role-playing game in the world (Alien Revolt) released in may 2004 with extensive press coverage. 
	\item Formulated the game structure, dynamics and mathematical framework 
	\item Managed the development team and assured the quality of every released item from developers and designers.
\end{itemize}
  
{\bf Getulio Vargas Foundation (FGV)} \hfill Rio de Janeiro, Brazil \\
{\sl Lead Game Developer} \hfill February 1998 - January 2000
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Managed a group of 11 developers, 12 designers and 3 musicians	
	\item Designed and implemented, using C/C++, the game physics, intelligence, sound and video. 
	\item Presented a lecture on the game engine technology to the Brazilian Ministry of Science and Technology.
\end{itemize}

\pagebreak

{\bf Ebendinger Corporations} \hfill Rio de Janeiro, Brazil \\
{\sl Systems Support} \hfill June 1996 - November 1997  
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Managed a database, using SQL, of over 80,000 physicians.
	\item Developed network and database scripts, using PERL, to add to the robustness of the database.
	\item Participated in the customer care team to users of the database.
\end{itemize}


\section{\centerline{RESEARCH EXPERIENCE}} 
\vspace{8pt}

{\bf Harvard University} \hfill Cambridge, MA \\
{\sl Research Assistant in Computational Biology} \hfill September 2005 - present 
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Developed a statistical method, in C and LUA, to describe the evolution of fitness landscapes.
	\item Developed a Markov Chain model, in C, to describe gene network development and evolution.
	\item Developed scripts, in LUA, to aid in the fruit fly genome annotation project. 
	\item Developed the BIOLUA library, in C and LUA, to determine the evolutionary patterns of amino-acid secondary structure.
\end{itemize}

{\bf Oswaldo Cruz Research Institute (FIOCRUZ)} \hfill Rio de Janeiro, Brazil \\
{\sl Junior Researcher in Molecular Epidemiology} \hfill March 2003 - August 2004  
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Developed a simulator (clockgen), in C, that generates random nucleotide sequences based on the theory of the existence of a molecular clock
	\item Studied Bioinformatics and Population Dynamics at the Pure and Applied Mathematics Institute of Rio de Janeiro (IMPA). 
	\item Developed a research project on HIV Evolution which was awarded with a full scholarship from the UCSD Medical School at the XI HIV Dynamics and Evolution Workshop, in Sweden - May 2004.
\end{itemize}

{\bf TECGRAF (PUC-RJ)} \hfill Rio de Janeiro, Brazil \\
{\sl Junior Researcher in Computer Graphics} \hfill March 2000 - March 2003  
\begin{itemize} \itemsep -2pt % reduce space between items
	\item Developed research on multi-platform libraries and tools. 
	\item Developed 2 LUA libraries (IUPLUA and LUASSL), 1 sound and multimedia project and a user interface toolkit (IUP) in C/C++. 
\end{itemize}


\section{\centerline{PUBLICATIONS}} 
\vspace{8pt}


1000 Genomes Consortium. 2012. An integrated map of genetic variatoin in 1,092 human genomes. Nature - 491:56-65


{\bf Carneiro M}, Russ C, Ross MG, Gabriel S, Nusbaum C, DePristo MA. 2012. Pacific biosciences sequencing technology for genotyping and variation discovery in human data - BMC Genomics 2012, 13:375


Pugh TJ, Weeraratne SD, Archer TC, Krummel DA, Auclair D, Bochicchio J, {\bf Carneiro M} et al. 2012. Medulloblastoma exome sequencing uncovers subtype-specific somatic mutations. Nature 488:106-110


{\bf Carneiro M}, Hartl DL. 2011. Model transcription networks with continuously varying expression levels. BMC Evolutionary Biology - Accepted. In Press.


{\bf Carneiro M}, Hartl DL. 2010. Adaptive landscapes and protein evolution. Proceedings of the National Academy Sciences USA 107:1747-51.


Sackton T, ..., {\bf Carneiro M} et al. 2009. Population genomic inferences from sparse high-throughput sequencing of two populations of Drosophila melanogaster. Genome Biology and Evolution, 449 - 465.


{\bf Carneiro M}, Pinto M, Struchiner CJ. 2004. Analysis of the molecular clock hypothesis for the brazilian HIV-I subtype. In Proceedings of the 11th International Workshop on HIV Dynamics and Evolution
  

\section{\centerline{TEACHING EXPERIENCE}} 
\vspace{8pt}

{\bf Harvard University} \hfill Cambridge, MA\\
Modeling and Differential Equations (fall 06, 07, 08, 09 and 10, spring 09 and \textit{teaching award} in 10), Intensive Introduction to Computer Science (summer 08, 09), Intensive Introduction to Data Structures (summer 08, 09), Dinosaurs and their Relatives (\textit{teaching award} - spring 2008), Genetics, Genomics and Evolution (spring 2007)

{\bf PUC-RJ, FIOCRUZ and Technology \& Training} \hfill Rio de Janeiro, Brazil\\
Advanced Topics in Algorithms (2003), Interactive Computer Graphics (2001), Data Structures (2000-2001),  Evolutionary Basis of Public Health (2003), Game Development (2004).

\section{\centerline{LEADERSHIP EXPERIENCE}} 
\vspace{8pt}

{\bf Harvard University Graduate Soccer Team} \hfill Cambridge, MA\\
{\sl GSAS Soccer Team Captain} \hfill 2006 -  2010\\
{\sl Dudley Soccer Team Captain} \hfill 2006 -  2010

\vspace{-10pt}
{\bf Harvard Organization for Brazilian Leadership and Entrepreneurship} \hfill Cambridge, MA\\
{\sl Co-Founder and Vice-President} \hfill 2008 - 2010

\section{\centerline{ADDITIONAL COURSES}} 
\vspace{8pt}

{\bf University of Washington} \hfill Seattle, WA\\
{\sl Summer Institute in Statistical Genetics} \hfill 2006 and 2007

\vspace{-10pt} 
{\bf Pure and Applied Mathematics Institute (IMPA)} \hfill Rio de Janeiro, Brazil\\
{\sl International Workshop in Biomathematics} \hfill 2004

\vspace{-10pt} 
{\bf Sao Luiz Info School } \hfill Rio de Janeiro, Brazil\\
{\sl Introduction to Pascal} \hfill 1987\\
{\sl Advanced Basic Programming} \hfill 1986\\
{\sl Introduction to Basic Programming} \hfill 1986\\

\end{resume} 
\end{document}













